(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-26 ms.tex
Started 3.2

\begin{abstract}
\btmtodo{This is where the abstract will go}
\end{abstract}

@@

\btmtodo{Some of Mann's references aren't in his .bib file. Fix.}

@@

@@

\subsection{Known Background Stars}

@@

Some of the data presented in this paper were obtained from the Mikulski
Archive for Space Telescopes (MAST). 
STScI is operated by the Association of Universities for Research 
in Astronomy, Inc., under NASA contract NAS5--26555. 
for MAST for non--HST data is provided by the NASA Office of Space 
Science via grant NNX13AC07G and by other grants and contracts. 
This paper includes data collected by the \kep\ mission. 
Funding for the \kep\ mission is provided by the NASA Science 
Mission directorate.

>>>>

\begin{abstract}
\btmtodo{This is where the abstract will go}
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\end{abstract}

@@

@@

This is Brendan.

\subsection{Known Background Stars}
The P3K AO system has a field of view of $3.84 \times 3.84$ arcseconds.
\btmtodo{Check with Brendan to make sure he used this mode}.
Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds. 
A background eclipsing binary within a few \KT\ pixels of our target 
stars could mimic a transit signal while evading detection by P3K.
Such wide eclipsing binaries should appear in seeing-limited ground-based
surveys.

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey 
\citep[SDSS DR9,][]{Ahn12}. For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.

@@

This is Ben.

@@

Some of the data presented in this paper were obtained from the Mikulski
Archive for Space Telescopes (MAST). 
STScI is operated by the Association of Universities for Research 
in Astronomy, Inc., under NASA contract NAS5--26555. 
for MAST for non--HST data is provided by the NASA Office of Space 
Science via grant NNX13AC07G and by other grants and contracts.

This paper includes data collected by the \kep\ mission. 
Funding for the \kep\ mission is provided by the NASA Science 
Mission directorate.

This paper includes data collected by the Sloan Digital Sky Survey.
Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation,
the Participating Institutions, the National Science Foundation, and the
U.S. Department of Energy Office of Science. The SDSS-III web site is
http://www.sdss3.org/.
SDSS-III is managed by the Astrophysical Research Consortium for the
Participating Institutions of the SDSS-III Collaboration including the
University of Arizona, the Brazilian Participation Group, Brookhaven
National Laboratory, Carnegie Mellon University, University of Florida,
the French Participation Group, the German Participation Group, Harvard
University, the Instituto de Astrofisica de Canarias, the Michigan
State/Notre Dame/JINA Participation Group, Johns Hopkins University,
Lawrence Berkeley National Laboratory, Max Planck Institute for
Astrophysics, Max Planck Institute for Extraterrestrial Physics, New
Mexico State University, New York University, Ohio State University,
Pennsylvania State University, University of Portsmouth, Princeton
University, the Spanish Participation Group, University of Tokyo,
University of Utah, Vanderbilt University, University of Virginia,
University of Washington, and Yale University.
